---
title: "Two Parameters"
author: "Grant Quattlebaum"
format: html
execute:
  echo: false
  warning: false
---

```{r}
#| message: false

library(tidyverse)
library(primer.data)
library(tidybayes)
library(brms)
library(gtsummary)
```

```{r}
nhanes |> filter(sex == "Male", age >= 18) |>
  select(height) |>
  drop_na() |>
  ggplot(aes(x = height)) +
  geom_histogram(bins = 50) +
  labs(
    title = "Male Adult Height in US from 2009-2011",
    caption = "Source NHANES 2009-2011",
    x = "Height",
    y = "Count")
```

```{r}
ch5 <- nhanes |> filter(sex == "Male", age >= 18) |>
  select(height)
```

```{r}
#| cache: true

fit_male_height <- brm(formula = height ~ 1, data = ch5, family = gaussian(), silent = 2, refresh = 0, seed = 12)
```

```{r}
#| label: plot

fit_male_height |> 
  add_predicted_draws(newdata = tibble(.rows = 1)) |>
  ggplot(aes(x = .prediction)) +
    geom_histogram(aes(y = after_stat(count/sum(count))), bins = 100) +
    labs(
      title = "Height Distribution of Random Adult Men",
      subtitle = "A random man is at least 180 cm tall less than half the time",
      x = "Height",
      y = "Proportion",
      caption = "Source: NHANES, 2009-2011") +
    scale_x_continuous(labels = scales::number_format()) + 
    scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

We're using height data collected in the NHANES from 2009 to 2011 to build a model for the height of adult men that can answer questions like "Given 4 random men, what would the biggest difference in their heights be on average?". Our data represents a broad cross-section of America, but changes in demographics since 2010 may limit its applicability. We modeled the height using a linear intercept-only regression with an error term in the Gaussian family. We found that average male height was 175.9 cm with a standard deviation of 7.5, though realistically this answer applies to American men: you'd likely get a different answer altogether if you surveyed men from Denmark or Japan.

```{r}
tbl_regression(fit_male_height, intercept = TRUE)
```

```{r}
fit_male_height |> add_predicted_draws(newdata = tibble(.rows = 1)) |>
  mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |>
  summarize(odds = mean(tall))
```

